\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage[noadjust]{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{array,etoolbox,multirow}
\usepackage{float}
\usepackage{caption} 
\usepackage{multirow}
\captionsetup[table]{skip=6pt}


\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Interview Guide for the Paper Titled: Application of Microservices Patterns to Big Data Systems\\
% {\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
% should not be used}
% \thanks{Identify applicable funding agency here. If none, delete this.}
}

% \author{\IEEEauthorblockN{1\textsuperscript{st} Pouya Ataei}
% \IEEEauthorblockA{\textit{School of Engineering, Computer and Mathematical Science} \\
% \textit{Auckland University of Technology}\\
% Auckland, New Zealand \\
% pouya.ataei@aut.ac.nz}
% \and
% \IEEEauthorblockN{2\textsuperscript{nd} Daniel Staegemann}
% \IEEEauthorblockA{\textit{Magdeburg Research and Competence Cluster VLBA} \\
% \textit{Otto-von-Guericke University Magdeburg}\\
% Magdeburg, Germany \\
% daniel.staegemann@ovgu.de}}

\maketitle

\subsection{Introduction}

Thanks for your participation. We are interviewing you to validate our theories in regards to application of microservices patterns to big data systems. There are no right or wrong answers, and we are really interested in your opinion and experiences. 

The interview should take approximately one hour depending on the flow of our dialogues. With you permission I will be recoding this interview because I don't want to miss any valuable information. This recording will be shared with my research team for further analysis. 

All your responses will be confidential, and the results of this interview will be presented without mentioning your name. The interview should take approximately one hour depending on how much information you would like to share. 

You may decline to answer any question or stop the interview at any
time and for any reason. Are there any questions about what I have just explained?ion of any individual name. Should you wish to not answer any of the questions, you may decline the question or stop the interview at any time. 

Are there any questions in regards to what I have just explained ?

\hspace{2cm}

\textbf{Note to the reader/researcher:} Please not that this guide aims to only encompass the main themes being discussed with the interviewee and as such does not include the prompts that may have emerged in the process of interview. Some general prompts and close-ended questions are included.


\subsection{\textbf{Establishing Rapport}}

Before the interview begin, it would be nice if you could introduce yourself and tell me a bit about your background and your area of interest. 

\subsection{\textbf{Candidates background}}

\begin{enumerate}
    \item Could you please tell me your job title ? 
    \item Could you please tell me how many years of professional experience have you got in software engineering or data engineering ? 
    % \item Could you please tell me in which level of proficiency do you consider yourself to be ? (answer from 1 to 5, 1 being novice, and 5 being expert)
\end{enumerate}

\subsection{\textbf{Familiarity with big data systems}}

\begin{enumerate}
    \item Could you please tell how many years of experience have you got related to data engineering or big data ?
    \item Could you please elaborate on your experience/s with big data systems ( or any related systems ) ? 
    % \item Are you familiar with challenges of big data system development ?
\end{enumerate}


\subsection{\textbf{Familiarity with Microservices}}

\begin{enumerate}
    \item Could you please tell how many years of experience have you got related to microservices architecture ?
    \item Could you please elaborate on your experience/s with microservices architecture ( or any related systems ) ?
    % \item Are you familiar with challenges of microservices architecture ?
\end{enumerate}


\subsection{\textbf{Microservices patterns for big data systems}}

\begin{enumerate}
    \item How do you find the mapping of the patterns to the mentioned characteristics ? 
    \item Overall, do you think the concepts discussed could be helpful to practitioners or academics ?  
    \item Do you see any limitations with our study ? 
    \item Have we missed any pattern for any problem ?
\end{enumerate}

\subsection{\textbf{Closing thoughts}}

\begin{enumerate}
    \item Are there any further comments/suggestions/improvements that you have got for our study ?
\end{enumerate}

\end{document}
        